---
title: "Flexdashboard"
author: "Max Kruisbrink"
output: 
  flexdashboard::flex_dashboard:
    favicon: "20220808_maxplaining-logo-48x48.jpg"
    orientation: rows
    social: menu
---


```{r setup, include=FALSE}

#libraries
library(ggplot2)
library(plotly)
library(plyr)
library(flexdashboard)
library(pilot)
library(tidyverse)
library(here)
library(scales)
library(reactable)



### Nomics.com
### Nomics.com
### Nomics.com


#read historical market capitalization
df_hist_mcap <- read_csv("../portfolio-tracker/data/hist-mcap.csv")

#read histoical market volume
df_hist_vol <- read_csv("../portfolio-tracker/data/hist-vol.csv")

#read Bitcoin monthly data
btc_candles_monthly <- read_csv("../portfolio-tracker/data/bitcoin-candles.csv")

#read global ticker data
global_ticker <- read_csv("../portfolio-tracker/data/global-ticker.csv")

#read currencies ticker data
currencies_ticker <- read_csv("../portfolio-tracker/data/currencies-ticker.csv")

webscraped_active_projects <-  read_csv("data/ticker-data-webscraping.csv")



### CBS (other R-project)
### CBS (other R-project)
### CBS (other R-project)


#consumer trust
consumer_trust <- read_csv("../cbs-open-data/data/83694NED_consumertrust-economicclimate.csv")

#fuel prices
fuel_prices <- read_csv("../cbs-open-data/data/80416NED_brandstofprijzen.csv")

#consumer price index (inflation)
CPI <- read_csv("../cbs-open-data/data/70936NED_CPI-month.csv")


### Third party sources
### Third party sources
### Third party sources


#read fear & greed index
fear_greed <- read_csv("data/fear-greed.csv")


#stock data
stocks_vs_crypto <- read.csv("data/stocks-vs-crypto.csv")

```


Sidebar {.sidebar}
=======================================================================

This `flexdashboard` is made with *R markdown* (`.Rmd`) and uses several API services such as [Nomics.com](https://p.nomics.com/cryptocurrency-bitcoin-api) while webscraping for other relevant data. 

The dashboard should be considered a ***work in progress*** and will be updated regularly. 

**Some planned features include:**

* fully automated (daily) updates
* interactive historic time series (shiny)
* dead & inactive coins
* additional metrics & charts
* change % heatmaps
* additional on-chain analysis
* sentiment analysis
* economic indicators

I have loads of plans for this dashboard and might create multiple dashboard as this one grows in size.

email: [max@cryptocommunity.nl](mailto:max@cryptocommunity.nl)
 
Active Projects
=======================================================================

Row
-------------------------------------

### Refresh Timestamp
```{r}
valueBox(Sys.Date(),
         icon = "fa-calendar")
```

```{r include=FALSE}
active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
```


### Platform Currencies
```{r}

valueBox(value = length(active_projects$platform_currency),
         icon = "fa-hashtag"
         )
```



### Active Projects on ETH
```{r}

valueBox(value = active_projects %>% 
           filter(platform_currency == "ETH") %>% 
           select(count),
         icon = "fa-hashtag")
```

### Active Projects on BNB
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(value = active_projects %>% 
           filter(platform_currency == "BNB") %>% 
           select(count),
         icon = "fa-hashtag")
```


### Active SOLO projects

```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(value =  active_projects %>% 
           filter(is.na(platform_currency)) %>% 
           select(count),
         icon = "fa-hashtag"
         )
```


### Active Projects on MATIC
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(active_projects %>% 
           filter(platform_currency == "MATIC") %>% 
           select(count),
         icon = "fa-hashtag")
```


### Active Projects on SOL
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(active_projects %>% 
           filter(platform_currency == "SOL") %>% 
           select(count),
         icon = "fa-hashtag")
```



Row {.tabset .tabset-fade}
-------------------------------------

### Active Projects

```{r reactable, cache=TRUE}

library("reactablefmtr")

webscraped_active_projects %>% 
  reactable(
    defaultColDef = colDef(
      align = "center",
      headerStyle = list(background = "#f7f7f8"),
    ),
    searchable = TRUE, 
    defaultPageSize = 100,
    bordered = TRUE,
    highlight = TRUE,
    defaultSorted = c("rank"),
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
    
    columns = list(
    logo_url = colDef(name = "Logo",
                      cell = embed_img(logo_url)),
    rank = colDef(name = "Rank"),
    rank_delta = colDef(name = "Rank Change",
                        style = pos_neg_colors("red", "green", bold = TRUE)),
    name = colDef(name = "Name"),
    id = colDef(name = "ID"),
    price = colDef(name = "Price",
                   format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 2,)),
    high = colDef(name = "Highest Price",
                  format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 2)),
    price_pct_ath = colDef(name = "Price % from ATH",
                           format = colFormat(suffix = "%",
                                      digits = 1),
                           style = color_scales(., colors = c('#ff0000', '#ffa700', '#fff400', "#a3ff00", "#2cba00"), 
                                                bold_text = TRUE)),
    high_timestamp = colDef(name = "ATH Timestamp",
                            format = colFormat(date = TRUE)
                            ),
    days_ath = colDef(name = "Days since ATH"),
    circulating_supply = colDef(name = "Circulating Supply"),
                                
    max_supply = colDef(name = "Max Supply"),
    market_cap = colDef(name = "Market Cap",
                        format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 0)
                  ),
    market_cap_dominance = colDef(name = "Market Cap Dominance",
                                  format = colFormat(suffix = "%",
                                  digits = 1)
                   ),
    num_exchanges = colDef(name = "Number of Exchanges"),
    num_pairs = colDef(name = "Number of Pairs"),
    platform_currency = colDef(name = "Platform Currency")
  
  ))

```

### Price Change %

```{r price change percent portfolio, cache=TRUE}

library("reactablefmtr")


currencies_ticker %>% select(logo_url,
                      "1d_price_change_pct",
                      "7d_price_change_pct",
                      "30d_price_change_pct",
                      "365d_price_change_pct",
                      "ytd_price_change_pct") %>% 
  reactable(
    defaultColDef = colDef(
      format = colFormat(percent = TRUE,
                         separators = TRUE,
                         digits = 1),
      align = "center",
      headerStyle = list(background = "#f7f7f8"),
      style = pos_neg_colors("red", "green", 
                             bold = TRUE),
      ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
      columns = list(
         logo_url = colDef(name = "Logo",
                           cell = embed_img(logo_url))
         )
  )

```



Global Data {data-orientation=rows}
=======================================================================

Row
-------------------------------------

### Time Stamp
```{r}
valueBox(currencies_ticker$price_timestamp[1],
         icon = "fa-calendar")
```


### Total Number of Projects
```{r}
valueBox(global_ticker$num_currencies,
         icon = "fa-hashtag")
```

### Total Number of Active Projects
```{r}
valueBox(global_ticker$num_currencies_active,
         icon = "fa-hashtag")
```

### Total Number of Inactive Projects
```{r}
valueBox(global_ticker$num_currencies_inactive,
         icon = "fa-hashtag")
```

### Total Number of Dead Projects
```{r}
valueBox(global_ticker$num_currencies_dead,
         icon = "fa-hashtag")
```

### Total Number of New Projects
```{r}
valueBox(global_ticker$num_currencies_new,
         icon = "fa-hashtag")
```



Row {.tabset .tabset-fade}
-------------------------------------

### Status of All Cryptocurrency Projects

```{r}

# Plot status of all cryptocurrency projects on nomics 
plot <- currencies_ticker %>% 
  ggplot(aes(status)) +
  geom_bar(fill="#FCC200",) +
  labs(x = "Status", 
       y = "Number of projects",
       #title ="Status of all Cryptocurrency Projects",
       subtitle = "Actively traded, inactive or dead",
       caption = "Data by nomics.com") + 
  theme_pilot() +
  theme(axis.title = element_text(),
        legend.text =  element_text(size=10)) +
  guides(fill = guide_legend(title = "Type")) +
  coord_flip() +
  scale_y_continuous(labels = scales::label_number_si())

ggplotly(plot)

```

### Amount of Cryptocurrency Projects by Platform 

```{r}

plot <- currencies_ticker %>% group_by(platform_currency) %>% 
  filter(n() >= 100) %>%
  ggplot(aes(platform_currency, fill=status)) +
  geom_bar() + 
  labs(x = FALSE, 
       y = "Count",
       #title ="Amount of Cryptocurrency Projects by Platform",
       subtitle = "Actively traded, inactive or dead",
       caption = "Data by Nomics.com") + 
  coord_flip() +
  theme_pilot()

ggplotly(plot)

```

### Status of All Cryptocurrency Projects

```{r}

plot <- currencies_ticker %>% 
  group_by(platform_currency) %>% 
  filter(n() >= 100) %>%
  ggplot(aes(status, fill = platform_currency)) +
  geom_bar(position = "stack") +
  labs(x = "Status", 
       y = "Number of projects",
       #title ="Amount of Active, Inactive and Dead Projects",
       subtitle = "Status by platform (N > 100)",
       caption = "Data by Nomics.com") +
  theme_pilot() +
  coord_flip() +
  scale_y_continuous(labels = scales::label_number_si()) +
  theme(axis.title = element_text(),
        legend.text =  element_text(size=10),
        legend.key.size = unit(.5, 'cm')) +
  guides(fill = guide_legend(title = "Type"))

ggplotly(plot)

```




Market Charts {data-orientation=rows}
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### Historical Market Capitalization

```{r}

# Mean monthly market cap
monthly_mcap <- df_hist_mcap %>% 
  group_by(monthly) %>% 
  summarise(market_cap = mean(market_cap))
  
hist_mcap <- monthly_mcap %>%
  ggplot(aes(monthly,market_cap)) +
  geom_point(color = "red",
             size = .8) +
  geom_line(color = "red") +
  labs(x = NULL, #year is obvious
       y = "Market Cap ($)",
       #title ="Historical Cryptocurrency Market Cap",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year",
               date_minor_breaks = "1 month") + 
  scale_y_log10(breaks = log_breaks(10),
                labels = label_number(scale_cut = cut_short_scale())) +
  annotation_logticks() +
  theme_pilot()

ggplotly(hist_mcap) 


```


### Historical Market Volume

```{r}


# Mean monthly volume
monthly_vol <- df_hist_vol %>% 
  group_by(monthly) %>% 
  summarise("mean_volume" = mean(volume),
            "mean_spot_volume" = mean(spot_volume),
            "mean_derivative_volume" = mean(derivative_volume)) 

hist_vol <- monthly_vol %>%
  ggplot(aes(monthly, mean_volume)) +
  geom_point(color = "red",
             size = .8) +
  geom_line(color = "red") +
  labs(x = NULL, #year is obvious
       y = "Market Cap ($)",
       #title ="Historical Cryptocurrency Market Cap",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year",
               date_minor_breaks = "1 month") + 
  scale_y_log10(breaks = log_breaks(10),
                labels = label_number(scale_cut = cut_short_scale())) +
  annotation_logticks() +
  theme_pilot()

ggplotly(hist_vol)

```




Bitcoin Charts {data-orientation=rows}
=====================================     
   
Row {.tabset .tabset-fade}
-------------------------------------

### Bitcoin 200 Week Moving Average (MA) Heatmap


```{r}
btc_graph <- btc_candles_monthly %>% ggplot(aes()) + 
  geom_line(aes(timestamp, 
                close)) +
  geom_point(aes(timestamp, 
                 close, 
                 colour = `1400D_MA_change`)) +
  geom_line(aes(timestamp, `1400D_MA`), 
            color = "red") + 
  scale_colour_gradientn(colours = rainbow(5)) +
  labs(x = "Year", 
       y = "Closing Price",
       #title ="200 Week Moving Average Heatmap",
       subtitle = expression(`200 WMA Heatmap = 4-weekly % change in MA`["1400"]),
       caption = "Source: Crypto Market Cap & Pricing Data Provided By Nomics") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year") +
  scale_y_log10(labels = label_dollar(suffix = "€", 
                                       prefix = "")) +
  theme_pilot() 


ggplotly(btc_graph)


```


### Bitcoin 2-Year Moving Average (MA) Multiplier


```{r}

# Plotting Close and 2Y MA + 2Y MA * 5
btc_graph <- btc_candles_monthly %>% ggplot(aes(x = timestamp)) +
  
  geom_line(aes(y = close)) +
  geom_line(aes(y = `2Y_MA`, 
                color = "2Y_MA"),
            linetype = "dotdash") +
  geom_line(aes(y = `2Y_MA*5`, 
                color = "2Y_MA*5"),
            linetype = "dotdash") +
  scale_color_manual(name = "Moving Averages", 
                     values = c("2Y_MA*5" = "red", 
                                "2Y_MA" = "blue")) +
    labs(x = "Year", 
       y = "Closing Price",
       #title ="Bitcoin 2-Year MA Multiplier",
       subtitle = expression(`MA[730] and MA[730*5]`),
       caption = "Source: Crypto Market Cap & Pricing Data Provided By Nomics") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year") +
  scale_y_log10(labels = dollar_format(suffix = "€", 
                                       prefix = "")) +
  scale_fill_discrete(name = "MA", labels = c("2Y MA", "2Y MA * 5")) +
  theme_pilot()
  
#Save as HTML widget
ggplotly(btc_graph)


```


### Stocks vs. Crypto Charts


```{r}

# plot from origin
plot <- stocks_vs_crypto %>%
  ggplot(aes(as.Date(date), 
             price_index, 
             color = symbol)) + 
  geom_line(size=.5) +
  labs(x = "Date", 
       y = "Indexed Price Performance") +
       #title ="Price Performance of DEX Tokens",
       #subtitle = "Crypto Market Cap & Pricing Data Provided By Nomics.") +
  scale_y_log10() +
  #scale_x_date(name="Month", date_breaks="3 month", minor_breaks=NULL, date_labels="%b-%Y") +
  #theme_fivethirtyeight() +
  theme_pilot() +
  guides(fill = guide_legend(title = "Type"))


ggplotly(plot)

```



Fear & Greed
=======================================================================

```{r include=FALSE}

### Required mutations

fg_counts <- data.frame(table(fear_greed$value_classification))
fg_counts

# Change column names
colnames(fg_counts) <- c('Label', 'Count')

# Reorder Categories (Extreme Fear to Extreme Greed):
fg_counts$Label <- factor(fg_counts$Label, 
                          label = c("Extreme Fear", "Fear", "Neutral", "Greed", "Extreme Greed"))

```


Row {.tabset .tabset-fade}
-------------------------------------


### Fear & Greed Index (Line Chart)


```{r}

fear_greed %>% 
  plot_ly(x = ~timestamp, y = ~value, type = 'scatter', mode = 'lines') %>%
  layout(xaxis = list(title = "\n Date"),
         yaxis = list(title = "Index Value \n"))

```


### Fear & Greed Index (Scatter Plot)


```{r}

fig <- plot_ly(data = fear_greed,
               type = 'scatter',
               x = ~timestamp, 
               y = ~value, 
               color = ~value_classification) %>% 
  layout(xaxis = list(title = "\n Date"),
         yaxis = list(title = "Index Value \n"))

fig


```


Column {data-width=400}
-------------------------------------


### Fear & Greed Index (Bar Chart) - Days Since 01-02-2018


```{r}
fg_bargraph <- fg_counts %>% 
  plot_ly(x = ~Label, y = ~Count,
          #name = "Fear & Greed Index Counts \n Since Feb 1, 2018", 
          type = "bar",
          text = ~Count, textposition = 'auto',
          marker = list(color = c('rgba(222,45,38,0.8)', 'rgba(206, 140, 104, 1)',
                                  'rgba(216, 211, 105, 1)', 'rgba(178, 212, 122, 1)',
                                  'rgba(83, 124, 17, 1)'))) %>%
  layout(xaxis = list(title = "\n Label"),
         yaxis = list(title = "No. Days \n"))

fg_bargraph

```


### Fear & Greed Index (Pie Chart)

```{r}
fg_piechart <- fg_counts %>%
  plot_ly(#name = "Fear & Greed Index From Feb 1, 2018 To Aug 27, 2021", 
          type = 'pie',
          labels = ~Label, values = ~Count,
          textinfo='label+percent+value',
          insidetextorientation='radial')  %>%
  layout()

fg_piechart


```






Statistics Netherlands (CBS) {data-orientation=rows}
=======================================================================




Row {.tabset .tabset-fade}
-------------------------------------

### Consumer Trust

```{r}
invasion <- lubridate::ymd('2022-02-24')

p1 <- consumer_trust %>% 
  ggplot(aes(period, consumer_trust)) + 
  geom_line(color = "red") +
  geom_point(color = "blue") +
labs(x = "Date", #year is obvious
     y = "Trust Level (%)",
     #title ="Consumer Trust (Netherlands)",
     subtitle = "Monthly Aggregate",
     caption = "Data by CBS") +
  scale_y_continuous(limits = c(-100,100)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y",
               date_minor_breaks="3 months") +
  geom_vline(xintercept = invasion,
             linetype = "dashed") +
  theme_pilot()                     
                       
ggplotly(p1)

```


```{r}
p1 <- consumer_trust %>% 
  ggplot(aes(period, economic_climate)) + 
  geom_line(color = "red") +
  geom_point(color = "blue",
             size = "0.8") +
labs(x = "Date", #year is obvious
     y = "Trust Level (%)",
     #title ="Economic Climate (Netherlands)",
     subtitle = "Monthly Aggregate",
     caption = "Data by CBS") +
  scale_y_continuous(limits = c(-100,100)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y",
               date_minor_breaks="3 months") +
  theme_pilot()                     
                       
ggplotly(p1)

```


### Financial Situation (last 12 months)

```{r}
p1 <- consumer_trust %>% 
  ggplot(aes(period, finances_last12mo)) + 
  geom_line(color = "red") +
  geom_point(color = "blue",
             size = "0.8") +
labs(x = "Date", #year is obvious
     y = "Trust Level (%)",
     #title ="Financial Situation (Netherlands)",
     subtitle = "Monthly Aggregate",
     caption = "Data by CBS") +
  scale_y_continuous(limits = c(-100,100)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y",
               date_minor_breaks="3 months") +
  theme_pilot()                     
                       
ggplotly(p1)

```


### Financial Situation (coming 12 months)

```{r}
p1 <- consumer_trust %>% 
  ggplot(aes(period, finances_next12mo)) + 
  geom_line(color = "red") +
  geom_point(color = "blue",
             size = "0.8") +
labs(x = "Date", #year is obvious
     y = "Trust Level (%)",
     #title ="Financial Situation (Netherlands)",
     subtitle = "Monthly Aggregate",
     caption = "Data by CBS") +
  scale_y_continuous(limits = c(-100,100)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y",
               date_minor_breaks="3 months") +
  theme_pilot()                     
                       
ggplotly(p1)

```


### Fuel Prices

```{r}
# Mean monthly market cap
p1 <- fuel_prices %>% 
  ggplot(aes(Date, Price, color = Type)) +
  geom_line() +
  labs(x = "Date", #year is obvious
       y = "Price",
       #title ="Fuel Prices at Petrol Stations",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_y_continuous(labels = dollar_format(suffix = "€", 
                                       prefix = "")) +
  
  theme_pilot()

ggplotly(p1)

```



### Consumer Price Index (CPI) - Inflation

```{r}
p1 <- CPI %>% 
  select(Perioden, JaarmutatieCPI_1) %>% 
  ggplot(aes(Perioden, JaarmutatieCPI_1, 
             group = 1)) +
  #geom_point() +
  geom_line(color = "red") +
  geom_point(color = "blue",
             size = 0.6,
             alpha = 0.8) +
  labs(x = "Jaar",
       y = "Jaarmutatie CPI (%)",
       #title = " Consumer Price Index (CPI)",
       subtitle = "1963 januari - 2022 april",
       caption="bron: CBS (https://opendata.cbs.nl)"
       ) +
  scale_x_date(date_breaks = "10 year",
               date_labels = "%Y") + 
  theme_pilot()

ggplotly(p1)
```