---
title: "Flexdashboard"
author: "Max Kruisbrink"
output: 
  flexdashboard::flex_dashboard:
    favicon: "20220808_maxplaining-logo.jpg"
    orientation: rows
    social: menu
---


```{r setup, include=FALSE}

#libraries
library(ggplot2)
library(plotly)
library(plyr)
library(flexdashboard)
library(pilot)
library(tidyverse)
library(here)
library(scales)
library(reactable)



### Nomics.com
### Nomics.com
### Nomics.com


#read historical market capitalization
df_hist_mcap <- read_csv("../portfolio-tracker/data/hist-mcap.csv")

#read histoical market volume
df_hist_vol <- read_csv("../portfolio-tracker/data/hist-vol.csv")

#read Bitcoin monthly data
btc_candles_monthly <- read_csv("../portfolio-tracker/data/bitcoin-candles.csv")

#read global ticker data
global_ticker <- read_csv("../portfolio-tracker/data/global-ticker.csv")

#read currencies ticker data
currencies_ticker <- read_csv("../portfolio-tracker/data/currencies-ticker.csv")

webscraped_active_projects <-  read_csv("data/ticker-data-webscraping.csv")



### CBS (other R-project)
### CBS (other R-project)
### CBS (other R-project)


#consumer trust
consumer_trust <- read_csv("../cbs-open-data/data/83694NED_consumertrust-economicclimate.csv")

#fuel prices
fuel_prices <- read_csv("../cbs-open-data/data/80416NED_brandstofprijzen.csv")

#consumer price index (inflation)
CPI <- read_csv("../cbs-open-data/data/70936NED_CPI-month.csv")


### Third party sources
### Third party sources
### Third party sources


#read fear & greed index
fear_greed <- read_csv("data/fear-greed.csv")


#stock data
stocks_vs_crypto <- read.csv("data/stocks-vs-crypto.csv")

```


Sidebar {.sidebar}
=======================================================================

This `flexdashboard` is made with *R markdown* (`.Rmd`) and uses several API services such as [Nomics.com](https://p.nomics.com/cryptocurrency-bitcoin-api) while webscraping for other relevant data. 

The dashboard should be considered a ***work in progress*** and will be updated regularly. 

**Some planned features include:**

* fully automated (daily) updates
* interactive historic time series (shiny)
* dead & inactive coins
* additional metrics & charts
* change % heatmaps
* additional on-chain analysis
* sentiment analysis
* economic indicators

I have loads of plans for this dashboard and might create multiple dashboard as this one grows in size.

email: [max@cryptocommunity.nl](mailto:max@cryptocommunity.nl)
 
Active Projects
=======================================================================

Row
-------------------------------------

### Refresh Timestamp
```{r}
valueBox(Sys.Date(),
         icon = "fa-calendar")
```

```{r include=FALSE}
active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
```


### Platform Currencies
```{r}

valueBox(value = length(active_projects$platform_currency),
         icon = "fa-hashtag"
         )
```



### Active Projects on ETH
```{r}

valueBox(value = active_projects %>% 
           filter(platform_currency == "ETH") %>% 
           select(count),
         icon = "fa-hashtag")
```

### Active Projects on BNB
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(value = active_projects %>% 
           filter(platform_currency == "BNB") %>% 
           select(count),
         icon = "fa-hashtag")
```


### Active SOLO projects

```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(value =  active_projects %>% 
           filter(is.na(platform_currency)) %>% 
           select(count),
         icon = "fa-hashtag"
         )
```

### Active Projects on MATIC
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(active_projects %>% 
           filter(platform_currency == "MATIC") %>% 
           select(count),
         icon = "fa-hashtag")
```


### Active Projects on SOL
```{r}

active_projects <- webscraped_active_projects %>% 
                      group_by(platform_currency) %>% 
                      summarise(count = n())
            
valueBox(active_projects %>% 
           filter(platform_currency == "SOL") %>% 
           select(count),
         icon = "fa-hashtag")
```



Row {.tabset .tabset-fade}
-------------------------------------

### Active Projects

```{r reactable, cache=TRUE}

#merge full API data table with active scraped data
webscraped_active_projects <- inner_join(webscraped_active_projects, 
                   currencies_ticker %>% select(1,24:58), 
                   by = "id")

library("reactablefmtr")

webscraped_active_projects %>% 
  reactable(
    defaultColDef = colDef(
      align = "center",
      headerStyle = list(background = "#f7f7f8"),
    ),
    searchable = TRUE, 
    defaultPageSize = 100,
    bordered = TRUE,
    highlight = TRUE,
    defaultSorted = c("rank"),
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
    
    columns = list(
    logo_url = colDef(name = "Logo",
                      cell = embed_img(logo_url)),
    rank = colDef(name = "Rank"),
    rank_delta = colDef(name = "Rank Change",
                        style = pos_neg_colors("red", "green", bold = TRUE)),
    name = colDef(name = "Name"),
    id = colDef(name = "ID"),
    price = colDef(name = "Price",
                   format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 2,)),
    high = colDef(name = "Highest Price",
                  format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 2)),
    price_pct_ath = colDef(name = "Price % from ATH",
                           format = colFormat(suffix = "%",
                                      digits = 1),
                           style = color_scales(., colors = c('#ff0000', '#ffa700', '#fff400', "#a3ff00", "#2cba00"), 
                                                bold_text = TRUE)),
    high_timestamp = colDef(name = "ATH Timestamp",
                            format = colFormat(date = TRUE)
                            ),
    days_ath = colDef(name = "Days since ATH"),
    circulating_supply = colDef(name = "Circulating Supply"),
                                
    max_supply = colDef(name = "Max Supply"),
    market_cap = colDef(name = "Market Cap",
                        format = colFormat(prefix = "€", 
                                      separators = TRUE, 
                                      digits = 0)
                  ),
    market_cap_dominance = colDef(name = "Market Cap Dominance",
                                  format = colFormat(suffix = "%",
                                  digits = 1)
                   ),
    num_exchanges = colDef(name = "Number of Exchanges"),
    num_pairs = colDef(name = "Number of Pairs"),
    platform_currency = colDef(name = "Platform Currency")
  
  ))

```

> Active cryptocurrency projects. *Source: https://nomics.com/*

### Periodic Volumes

```{r periodic volumes portfolio, cache=TRUE}

library("reactablefmtr")

webscraped_active_projects %>% select(logo_url,
                      "1d_volume",
                      "7d_volume",
                      "30d_volume",
                      "365d_volume",
                      "ytd_volume") %>% 
  reactable(
    defaultColDef = colDef(
      format = colFormat(prefix = "€", 
                         separators = TRUE, 
                        digits = 0),
      align = "center",
      headerStyle = list(background = "#f7f7f8")
      ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    columns = list(
      logo_url = colDef(name = "Logo",
                        cell = embed_img(logo_url)
                        ),
      "1d_volume" = colDef(name = "1 Day Volume"),
      "7d_volume" = colDef(name = "7 Day Volume"),
      "30d_volume" = colDef(name = "30 Day Volume"),
      "365d_volume" = colDef(name = "365 Day Volume"),
      "ytd_volume" = colDef(name = "Year to Date Volume")
  ))

```

> Periodic aggregated trading volumes for all active projects. *Source: https://nomics.com/*

### Price Change %

```{r price change percent portfolio, cache=TRUE}

library("reactablefmtr")


webscraped_active_projects %>% select(logo_url,
                      "1d_price_change_pct",
                      "7d_price_change_pct",
                      "30d_price_change_pct",
                      "365d_price_change_pct",
                      "ytd_price_change_pct") %>% 
  reactable(
    defaultColDef = colDef(
      format = colFormat(percent = TRUE,
                         separators = TRUE,
                         digits = 1),
      align = "center",
      headerStyle = list(background = "#f7f7f8"),
      style = pos_neg_colors("red", "green", 
                             bold = TRUE),
      ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
      columns = list(
         logo_url = colDef(name = "Logo",
                           cell = embed_img(logo_url))
         )
  )

```


> Periodic price changes for all active projects. *Source: https://nomics.com/*

### Market Cap Change

```{r market cap change portfolio, cache=TRUE}

library("reactablefmtr")

webscraped_active_projects %>% select(logo_url,
                      "1d_market_cap_change",
                      "7d_market_cap_change",
                      "30d_market_cap_change",
                      "365d_market_cap_change",
                      "ytd_market_cap_change") %>% 
  reactable(
    defaultColDef = colDef(
    format = colFormat(prefix = "€", 
                       separators = TRUE, 
                      digits = 3),
    style = pos_neg_colors("red", "green", 
                             bold = TRUE),
    align = "center",
    headerStyle = list(background = "#f7f7f8")
  ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    # style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
      columns = list(
         logo_url = colDef(name = "Logo",
                      cell = embed_img(logo_url))
  ))

```

> Periodic market cap changes for all active projects. *Source: https://nomics.com/*


### Volume Change %

```{r volume change percent portfolio, cache=TRUE}

library("reactablefmtr")

webscraped_active_projects %>% select(logo_url,
                      "1d_volume_change_pct",
                      "7d_volume_change_pct",
                      "30d_volume_change_pct",
                      "365d_volume_change_pct",
                      "ytd_volume_change_pct") %>% 
  reactable(
    defaultColDef = colDef(
    format = colFormat(separators = TRUE,
                       percent = TRUE,
                       digits = 1),
    style = pos_neg_colors("red", "green", 
                             bold = TRUE),
    align = "center",
    headerStyle = list(background = "#f7f7f8")
  ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
      columns = list(
         logo_url = colDef(name = "Logo",
                      cell = embed_img(logo_url))
  ))

```

> Periodic volume change % for all active projects. *Source: https://nomics.com/*


### Market Cap Change %

```{r market cap change percent portfolio, cache=TRUE}

library("reactablefmtr")

webscraped_active_projects %>% select(logo_url,
                      "1d_market_cap_change_pct",
                      "7d_market_cap_change_pct",
                      "30d_market_cap_change_pct",
                      "365d_market_cap_change_pct",
                      "ytd_market_cap_change_pct") %>% 
  reactable(
    defaultColDef = colDef(
      format = colFormat(percent = TRUE,
                         separators = TRUE,
                         digits = 1),
      align = "center",
      headerStyle = list(background = "#f7f7f8"),
      style = pos_neg_colors("red", "green", 
                             bold = TRUE),
      ),
    defaultPageSize = 25,
    bordered = TRUE,
    highlight = TRUE,
    #style = list(fontFamily = "Montserrat, sans-serif", fontSize = "1rem"),
      columns = list(
         logo_url = colDef(name = "Logo",
                           cell = embed_img(logo_url))
         )
  )

```

> Periodic market cap change % for all active projects. *Source: https://nomics.com/*


Global Data {data-orientation=rows}
=======================================================================

Row
-------------------------------------

### Time Stamp
```{r}
valueBox(currencies_ticker$price_timestamp[1],
         icon = "fa-calendar")
```

### Total Number of Projects
```{r}
valueBox(global_ticker$num_currencies,
         icon = "fa-hashtag")
```

### Total Number of Active Projects
```{r}
valueBox(global_ticker$num_currencies_active,
         icon = "fa-hashtag")
```

### Total Number of Inactive Projects
```{r}
valueBox(global_ticker$num_currencies_inactive,
         icon = "fa-hashtag")
```

### Total Number of Dead Projects
```{r}
valueBox(global_ticker$num_currencies_dead,
         icon = "fa-hashtag")
```

### Total Number of New Projects
```{r}
valueBox(global_ticker$num_currencies_new,
         icon = "fa-hashtag")
```



Row {.tabset .tabset-fade}
-------------------------------------

### Status of All Cryptocurrency Projects

```{r}

# Plot status of all cryptocurrency projects on nomics 
plot <- currencies_ticker %>% 
  ggplot(aes(status)) +
  geom_bar(fill="#FCC200",) +
  labs(x = "Status", 
       y = "Number of projects",
       #title ="Status of all Cryptocurrency Projects",
       subtitle = "Actively traded, inactive or dead",
       caption = "Data by nomics.com") + 
  theme_pilot() +
  theme(axis.title = element_text(),
        legend.text =  element_text(size=10)) +
  guides(fill = guide_legend(title = "Type")) +
  coord_flip() +
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()))

ggplotly(plot)

```

> Active, inactive and 'dead' projects as listed by Nomics.com. Projects are considered active if a certain trading treshold is reached. *Source: https://nomics.com/*

### Amount of Cryptocurrency Projects by Platform 

```{r}

plot <- currencies_ticker %>% group_by(platform_currency) %>% 
  filter(n() >= 100) %>%
  ggplot(aes(platform_currency, fill=status)) +
  geom_bar() + 
  labs(x = FALSE, 
       y = "Count",
       #title ="Amount of Cryptocurrency Projects by Platform",
       subtitle = "Actively traded, inactive or dead",
       caption = "Data by Nomics.com") + 
  coord_flip() +
  theme_pilot()

ggplotly(plot)

```

> Proportion of active, inactive and dead projects for the main cryptocurrency platforms. *Source: https://nomics.com/*

### Status of All Cryptocurrency Projects (by platform)

```{r}

plot <- currencies_ticker %>% 
  group_by(platform_currency) %>% 
  filter(n() >= 100) %>%
  ggplot(aes(status, fill = platform_currency)) +
  geom_bar(position = "stack") +
  labs(x = "Status", 
       y = "Number of projects",
       #title ="Amount of Active, Inactive and Dead Projects",
       subtitle = "Status by platform (N > 100)",
       caption = "Data by Nomics.com") +
  theme_pilot() +
  coord_flip() +
  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale())) +
  theme(axis.title = element_text(),
        legend.text =  element_text(size=10),
        legend.key.size = unit(.5, 'cm')) +
  guides(fill = guide_legend(title = "Type"))

ggplotly(plot)

```

> Proportion of cryptocurrency platforms for all active, inactive and dead projects. *Source: https://nomics.com/*


Market Charts {data-orientation=rows}
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### Historical Market Capitalization

```{r}

# Mean monthly market cap
monthly_mcap <- df_hist_mcap %>% 
  group_by(monthly) %>% 
  summarise(market_cap = mean(market_cap))
  
hist_mcap <- monthly_mcap %>%
  ggplot(aes(monthly,market_cap)) +
  geom_point(color = "red",
             size = .8) +
  geom_line(color = "red") +
  labs(x = NULL, #year is obvious
       y = "Market Cap ($)",
       #title ="Historical Cryptocurrency Market Cap",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year",
               date_minor_breaks = "1 month") + 
  scale_y_log10(breaks = log_breaks(10),
                labels = label_number(scale_cut = cut_short_scale())) +
  # annotation_logticks() +
  theme_pilot()

ggplotly(hist_mcap) 


```

> Aggregated historical monthly market capitalization data on a logarithmic scale. *Source: https://nomics.com/*

### Historical Market Volume

```{r}


# Mean monthly volume
monthly_vol <- df_hist_vol %>% 
  group_by(monthly) %>% 
  summarise("mean_volume" = mean(volume),
            "mean_spot_volume" = mean(spot_volume),
            "mean_derivative_volume" = mean(derivative_volume)) 

hist_vol <- monthly_vol %>%
  ggplot(aes(monthly, mean_volume)) +
  geom_point(color = "red",
             size = .8) +
  geom_line(color = "red") +
  labs(x = NULL, #year is obvious
       y = "Market Cap ($)",
       #title ="Historical Cryptocurrency Market Cap",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year",
               date_minor_breaks = "1 month") + 
  scale_y_log10(breaks = log_breaks(10),
                labels = label_number(scale_cut = cut_short_scale())) +
  # annotation_logticks() +
  theme_pilot()

ggplotly(hist_vol)

```

> Aggregated historical monthly market volume data on a logarithmic scale. *Source: https://nomics.com/*


Bitcoin Charts {data-orientation=rows}
=====================================     
   
Row {.tabset .tabset-fade}
-------------------------------------

### Bitcoin 200 Week Moving Average (MA) Heatmap


```{r}
btc_graph <- btc_candles_monthly %>% ggplot(aes()) + 
  geom_line(aes(timestamp, 
                close)) +
  geom_point(aes(timestamp, 
                 close, 
                 colour = `1400D_MA_change`)) +
  geom_line(aes(timestamp, `1400D_MA`), 
            color = "red") + 
  scale_colour_gradientn(colours = rainbow(5)) +
  labs(x = "Year", 
       y = "Closing Price",
       #title ="200 Week Moving Average Heatmap",
       subtitle = expression(`200 WMA Heatmap = 4-weekly % change in MA`["1400"]),
       caption = "Source: Crypto Market Cap & Pricing Data Provided By Nomics") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year") +
  scale_y_log10(labels = label_dollar(suffix = "€", 
                                       prefix = "")) +
  theme_pilot() 


ggplotly(btc_graph)


```

> In each of its major market cycles, Bitcoin's price historically bottoms out around the 200 week moving average. This indicator uses a colour heatmap based on the % increases of that 200 week moving average. Depending on the month-by-month % increase of the 200 week moving average, a colour is assigned to the price chart. Historically, when we see orange and red dots assigned to the price chart, this has been a good time to sell Bitcoin as the market overheats. Periods where the price dots are purple and close to the 200 week MA have historically been good times to buy. *Source: https://nomics.com/*

### Bitcoin 2-Year Moving Average (MA) Multiplier


```{r}

# Plotting Close and 2Y MA + 2Y MA * 5
btc_graph <- btc_candles_monthly %>% ggplot(aes(x = timestamp)) +
  
  geom_line(aes(y = close)) +
  geom_line(aes(y = `2Y_MA`, 
                color = "2Y_MA"),
            linetype = "dotdash") +
  geom_line(aes(y = `2Y_MA*5`, 
                color = "2Y_MA*5"),
            linetype = "dotdash") +
  scale_color_manual(name = "Moving Averages", 
                     values = c("2Y_MA*5" = "red", 
                                "2Y_MA" = "blue")) +
    labs(x = "Year", 
       y = "Closing Price",
       #title ="Bitcoin 2-Year MA Multiplier",
       subtitle = expression(`MA[730] and MA[730*5]`),
       caption = "Source: Crypto Market Cap & Pricing Data Provided By Nomics") +
  scale_x_date(date_labels = "%Y",
               date_breaks = "1 year") +
  scale_y_log10(labels = dollar_format(suffix = "€", 
                                       prefix = "")) +
  scale_fill_discrete(name = "MA", labels = c("2Y MA", "2Y MA * 5")) +
  theme_pilot()
  
#Save as HTML widget
ggplotly(btc_graph)


```

> Buying Bitcoin when price drops below the 2yr MA (green line) has historically generated outsized returns. Selling Bitcoin when price goes above the 2yr MA x 5 (red line) has been historically effective for taking profit. *Source: https://nomics.com/*


### Stocks vs. Crypto Charts


```{r}

# plot from origin
plot <- stocks_vs_crypto %>%
  ggplot(aes(as.Date(date), 
             price_index, 
             color = symbol)) + 
  geom_line(size=.5) +
  labs(x = "Date", 
       y = "Indexed Price Performance") +
       #title ="Price Performance of DEX Tokens",
       #subtitle = "Crypto Market Cap & Pricing Data Provided By Nomics.") +
  scale_y_log10() +
  #scale_x_date(name="Month", date_breaks="3 month", minor_breaks=NULL, date_labels="%b-%Y") +
  #theme_fivethirtyeight() +
  theme_pilot() +
  guides(fill = guide_legend(title = "Type"))


ggplotly(plot)

```

> Just a reminder for when you want to invest in traditional stocks. Cryptocurrency such as BTC and ETH have vastly outperformed the major corporations such as Apple (and even Tesla) over the past years. *Source: https://nomics.com/ & https://finance.yahoo.com/*

Fear & Greed
=======================================================================

```{r include=FALSE}

### Required mutations

fg_counts <- data.frame(table(fear_greed$value_classification))
fg_counts

# Change column names
colnames(fg_counts) <- c('Label', 'Count')

# Reorder Categories (Extreme Fear to Extreme Greed):
fg_counts$Label <- factor(fg_counts$Label, 
                          label = c("Extreme Fear", "Fear", "Neutral", "Greed", "Extreme Greed"))

```


Row {.tabset .tabset-fade}
-------------------------------------


### Fear & Greed Index (Line Chart)


```{r}

fear_greed %>% 
  plot_ly(x = ~timestamp, y = ~value, type = 'scatter', mode = 'lines') %>%
  layout(xaxis = list(title = "\n Date"),
         yaxis = list(title = "Index Value \n"))

```

> Simple line chart of values for the Fear & Greed index as listed by alternative.me. *Source: https://alternative.me/crypto/fear-and-greed-index*

### Fear & Greed Index (Scatter Plot)


```{r}

fig <- plot_ly(data = fear_greed,
               type = 'scatter',
               x = ~timestamp, 
               y = ~value, 
               color = ~value_classification) %>% 
  layout(xaxis = list(title = "\n Date"),
         yaxis = list(title = "Index Value \n"))

fig


```

> Scatter plot with color highlighting the different phases of 'fear' or 'greed'. *Source: https://alternative.me/crypto/fear-and-greed-index*

Column {data-width=400}
-------------------------------------


### Fear & Greed Index (Bar Chart) - Days Since 01-02-2018


```{r}
fg_bargraph <- fg_counts %>% 
  plot_ly(x = ~Label, y = ~Count,
          #name = "Fear & Greed Index Counts \n Since Feb 1, 2018", 
          type = "bar",
          text = ~Count, textposition = 'auto',
          marker = list(color = c('rgba(222,45,38,0.8)', 'rgba(206, 140, 104, 1)',
                                  'rgba(216, 211, 105, 1)', 'rgba(178, 212, 122, 1)',
                                  'rgba(83, 124, 17, 1)'))) %>%
  layout(xaxis = list(title = "\n Label"),
         yaxis = list(title = "No. Days \n"))

fg_bargraph

```

> Bar chart listing the cumulative time we have spent in different phases. You can clearly see there has been a lot more of 'extreme fear' than there has been 'extreme greed'. *Source: https://alternative.me/crypto/fear-and-greed-index*

### Fear & Greed Index (Pie Chart)

```{r}
fg_piechart <- fg_counts %>%
  plot_ly(#name = "Fear & Greed Index From Feb 1, 2018 To Aug 27, 2021", 
          type = 'pie',
          labels = ~Label, values = ~Count,
          textinfo='label+percent+value',
          insidetextorientation='radial')  %>%
  layout()

fg_piechart


```

> Pie chart listing the cumulative time we have spent in different phases. You can clearly see there has been a lot more of 'extreme fear' than there has been 'extreme greed'. *Source: https://alternative.me/crypto/fear-and-greed-index*


Statistics Netherlands (CBS) {data-orientation=rows}
=======================================================================


Row {.tabset .tabset-fade}
-------------------------------------

### Consumer confidence, economic climate and willingness to buy; adjusted

```{r}


p1 <- consumer_trust %>% pivot_longer(consumer_trust:timeto_bigspend, 
                                        names_to = "indicator", 
                                        values_to = "values") %>% 
  ggplot(aes(period, values, color = indicator)) + 
  geom_line() +
  geom_point() +
  labs(x = "Date", #year is obvious
       y = "Trust Level (%)",
       #title ="Consumer Trust (Netherlands)",
       subtitle = "Monthly Aggregate",
       caption = "Data by CBS") +
  scale_y_continuous(limits = c(-100,100)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y",
               date_minor_breaks="3 months") +
  theme_pilot()                     

ggplotly(p1)

```
> Seasonally adjusted data on Dutch consumers' views and expectations regarding general economic developments and their own financial situation. The indicators can have a value from -100 (everyone answers negative) to +100 (everyone answers positive). With a value of 0, the proportion of pessimists equals the proportion of optimists. *Source: https://opendata.cbs.nl/statline/#/CBS/nl/dataset/83693NED*


### Pump prices motor fuels; fuel type, per day

```{r}
# Mean monthly market cap
p1 <- fuel_prices %>% 
  ggplot(aes(Date, Price, color = Type)) +
  geom_line() +
  labs(x = "Date", #year is obvious
       y = "Price",
       #title ="Fuel Prices at Petrol Stations",
       subtitle = "Monthly Aggregate",
       caption = "Data by Nomics.com") +
  scale_y_continuous(labels = dollar_format(suffix = "€", 
                                       prefix = "")) +
  
  theme_pilot()

ggplotly(p1)

```

> This table contains pump prices of motor fuels. It shows weighted average daily prices of gasoline (Euro95), diesel oil and LPG including VAT and excise duty. *Source: https://opendata.cbs.nl/statline/#/CBS/nl/dataset/80416NED*


### Periodic changes in Consumer Pprice Index; from 1963

```{r}
p1 <- CPI %>% 
  select(Perioden, JaarmutatieCPI_1) %>% 
  ggplot(aes(Perioden, JaarmutatieCPI_1, 
             group = 1)) +
  #geom_point() +
  geom_line(color = "red") +
  geom_point(color = "blue",
             size = 0.6,
             alpha = 0.8) +
  labs(x = "Jaar",
       y = "Jaarmutatie CPI (%)",
       #title = " Consumer Price Index (CPI)",
       subtitle = "1963 januari - 2022 april",
       caption="bron: CBS (https://opendata.cbs.nl)"
       ) +
  scale_x_date(date_breaks = "10 year",
               date_labels = "%Y") + 
  theme_pilot()

ggplotly(p1)
```

> This table shows changes (mutations) in the Consumer Price Index (CPI) from the time it was first published. The chart shows how the prices of goods and services for consumers develop over time. *Source: https://opendata.cbs.nl/statline/#/CBS/nl/dataset/70936NED*